\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage[scale=0.8]{geometry}

% Personal information
\name{Erling}{Devold}
\title{Researcher in Machine Learning and Computer Vision}
\email{erling.devold@icloud.com}
\homepage{erlingdevold.github.io}
\social[linkedin]{erlingdevold}

\begin{document}
\makecvtitle

%---------------------------------------------------------------------
% Profile
%---------------------------------------------------------------------
\section{Profile}
Researcher focused on self-supervised and multimodal representation learning for visual and acoustic data. My work spans foundational methods for patch-level understanding, multimodal fusion, and domain adaptation applied to marine imaging and environmental monitoring. I am particularly interested in how vision foundation models learn structure and semantics across modalities.

%---------------------------------------------------------------------
% Education
%---------------------------------------------------------------------
\section{Education}
\cventry{2018--2023}{M.Sc. in Computer Science}{UiT The Arctic University of Norway}{}{}{
Specialization in machine learning. Thesis: \textit{Through Space and Time} (\href{https://hdl.handle.net/10037/29564}{hdl})
}

%---------------------------------------------------------------------
% Experience
%---------------------------------------------------------------------
\section{Experience}
\cventry{2023--Present}{Researcher (M.Sc.)}{SINTEF AS, Tromsø}{}{}{
Leading development of deep learning methods for marine imaging and environmental monitoring. Focus areas include representation learning, multimodal vision, and acoustic data analysis.
\begin{itemize}
  \item Work-package lead in FHF project \textit{SannTrål}: real-time trawl catch monitoring with stereo imaging.
  \item Principal researcher in \textit{JellySafe}: detection and segmentation of barbed-wire jellyfish (\textit{Apolemia}).
  \item Contributor to EU Horizon \textit{ILIAD}: scalable machine learning for aquaculture risk assessment.
  \item Collaboration with NASA JPL in \textit{SubZeroSpace} for self-supervised acoustic imaging under ice.
\end{itemize}}

\cventry{2021--2022}{Engineer (Teaching Assistant)}{UiT Department of Computer Science}{}{}{
Developed AirBit2 microcontroller platform for STEM education; designed teaching modules in Python for sensor programming and data collection.}

%---------------------------------------------------------------------
% Selected Projects
%---------------------------------------------------------------------
\section{Selected Projects}
\cvitem{SannTrål (FHF)}{Work-package lead developing real-time trawl monitoring using stereo camera systems and foundation model adapters.}
\cvitem{JellySafe (FHF)}{Researcher on transformer-based segmentation of barbed-wire jellyfish and multimodal CLIP-style modeling.}
\cvitem{ILIAD (EU Horizon)}{Developing scalable ML pipelines for ocean monitoring using geospatial and environmental data fusion.}
\cvitem{SubZeroSpace (RCN/NASA)}{Self-supervised acoustic representation learning for under-ice exploration in collaboration with NASA JPL.}
\cvitem{Aktivitetsplanlegger (BUFDIR)}{Led development of accessible planner app using React and FastAPI for inclusive user interfaces.}

%---------------------------------------------------------------------
% Publications & Presentations
%---------------------------------------------------------------------
\section{Publications and Presentations}
\cvitem{2023}{\textbf{Through Space and Time}, M.Sc. Thesis, UiT The Arctic University of Norway.}
\cvitem{2025}{\textbf{EchoFlow} (under review, JOSS): a containerised workflow for Kongsberg EK80 echosounder data.}
\cvitem{2025}{\textbf{Automated detection of barbed-wire jellyfish (Apolemia sp.) in citizen science imagery}, Aquaculture Europe Conference.}

%---------------------------------------------------------------------
% Skills
%---------------------------------------------------------------------
\section{Skills}
\cvitem{Machine Learning}{PyTorch, DINOv2, MAE, CLIP, Swin-Transformer, Multiple Instance Learning}
\cvitem{Engineering}{Hydra, Dask, Docker, DVC, FiftyOne, FastAPI}
\cvitem{Software}{Python, TypeScript, React, Git, Linux}

%---------------------------------------------------------------------
% Languages
%---------------------------------------------------------------------
\section{Languages}
\cvitem{Norwegian}{Native}
\cvitem{English}{Fluent}

\end{document}

